Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes

### 2019-02-13 Paper/AgreementAttraction.tex
First model, and major restructuring of the directory structure.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Original default rstudio/pandoc latex file
%% upated by @jhollist 09/15/2014
%% inspired by @cboetting https://github.com/cboettig/template and
%% @rmflight blog posts:
%% http://rmflight.github.io/posts/2014/07/analyses_as_packages.html 
%% http://rmflight.github.io/posts/2014/07/vignetteAnalysis.html).  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Changes borrowed from @cboettig, added by @jhollist 
% A modified page layout 
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
\usepackage{lineno} % add 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Packages and layout changes by @jhollist 09/15/2014
\usepackage{ragged2e}
\usepackage[font=normalsize]{caption}
  \usepackage[singlespacing]{setspace}
\usepackage{parskip}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
  \rfoot{\today}
\lfoot{\thepage}
%%Changed default abstract width and added lines
\renewenvironment{abstract}{
  \hfill\begin{minipage}{1\textwidth}
  \rule{\textwidth}{1pt}\vspace{5pt}
  \normalsize
  \begin{justify}
  \bfseries\abstractname\vspace{5pt}
  \end{justify}}
  {\par\noindent\rule{\textwidth}{1pt}\end{minipage}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural
Morphemes}
\author{
Utku Turk
Pavel Logacev
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

% Left justification of the text: see https://www.sharelatex.com/learn/Text_alignment
% \usepackage[document]{ragged2e} % already in the latex template
\newcommand{\bleft}{\begin{flushleft}}
\newcommand{\eleft}{\end{flushleft}}

% multicols
\usepackage{multicol}
\usepackage{paracol}

% enumerated examples
\usepackage{enumitem}

% for linguistic examples &  interlinear glosses
\usepackage{gb4e}
\exewidth{(10.159)}
\noautomath
\let\eachwordone=\it

\usepackage{qtree}

% for figure and table side by side
\usepackage{floatrow}
\newfloatcommand{btabbox}{table}

%%Fix tightlist error: https://stackoverflow.com/questions/40438037/tightlist-error-using-pandoc-with-markdown
%%Added 2018-03-26 
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
%%%

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural
Morphemes
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Utku Turk \textsuperscript{*} \textsuperscript{1} 
Pavel Logacev \textsuperscript{1} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}Bogazici University, Department of Linguistics, Istanbul, Turkey\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

\end{singlespace}

\vspace{2mm}\hrule

In this paper, our objective is to explore the source of agreement
attraction effects in Turkish discovered by Lago (2018). The
interpretation of their finding is complicated by the fact that the
possessive form of all head nouns used in their stimuli are
morphologically ambiguous between possessive and accusative. In Turkish,
genitive can be productively used for marking the subject of an embedded
clause whereas accusative is rarely used for marking the subject. Due to
this mismatch in the frequency of usage of accusative and genitive,
which is used as a attractor in this experiment, as a controller, Lago
(2018)'s findings could potentially be explained with occasional shallow
processing. We have replicated Lago (2018)'s experiment with unambigious
head nouns, and we have found similar agreement attraction effects.
However, this may mean that participants engage in even more shallow
processing than we imagined. We postulate that participants solely check
for the presence of a \emph{-lAr} morpheme, while largely disregarding
the remainder of the sentence. We utilize an experiment design in which
we use a relative clause with or without plural agreement on the verb in
place of the genitive possessor since both verbal and nominal plural
morphemes are the same in Turkish, i.e.~the exponent of both is
\emph{-lAr}. If participants did, in fact, adopt a superficial
processing strategy, we would expect to find a number agreement
attraction effect similar in magnitude to that in Lago (2018). However,
if number attraction is not an artifact of shallow processing
strategies, we should expect to find no number attraction effects in
this experiment.

\vspace{3mm}\hrule

\emph{Keywords}: Turkish, agreement attraction, task effect, shallow
processing

\bleft

@@

\section{REPLICATON OF LAGO ET AL.
(2018)}\label{replicaton-of-lago-et-al.-2018}

In their study, Lago (2018) investigate the comprehension of
subject-verb agreement in Turkish-German bilinguals and Turkish
monolinguals. They use speeded acceptability judgments for the effects
of number attraction in Turkish. Their sentences make us of
genitive-possessive constructions in the subject position, where the
genitive is the attractor and the possessive is the head noun. They
manipulate the grammaticality of the sentence by changing the plural
morphology of the verb, and they also manipulate the plurality of the
attractor noun. In grammatical conditions, the subject and the verb both
bear singular morphology with no overt morpheme. Moreover, in the
ungrammatical conditions, the verb bears the overt \emph{-lAr} morpheme
whereas the subject is still singular as exemplified below.

\begin{exe}
\ex
\begin{xlist}
\ex \underline{Grammatical, SG attractor} \label{lago1}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singer's backup vocalist jumped on the stage non-stop.

\ex \underline{Grammatical, PL attractor} \label{lago2}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singers' backup vocalist jumped on the stage non-stop.

\ex \underline{Ungrammatical, PL attractor} \label{lago3}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singers' backup vocalist jumped on the stage non-stop.

\ex \underline{Ungrammatical, SG attractor} \label{lago4}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singer's backup vocalist jumped on the stage non-stop.
\end{xlist}
\end{exe}

@@

One hundred and seven Turkish speakers with a mean age of X were
recruited from Bogazici University in İstanbul. We did not collect
participants' knowledge of other languages; however, we verified that
Turkish is their native language and that they predominantly use it in
their daily lives. In the experiments, participants were asked to judge
the acceptability of experimental and filler sentences in Turkish. All
of the sentences were presented one word at a time in the center of the
screen for 500 ms per word unlike Lago (2018) and Wagers et al. (2009),
in which the duration was 300 ms per word. The experiment was run on a
web-based platform titled the Ibex Farm, and all of the documentation
can be found on our osf and github page.

@@

In \textsc{Figure} (1), the y-axis shows the percentage of
``acceptable'' answers, and the x-axis indicates whether or not the
sentences in that group are grammatical. Moreover, the linet ypes
indicate an attractor noun with overt plural morphology. As seen in the
figure, 22\% of the sentences with plural attractors and a singular verb
were accepted by the participants, in line with the findings of Lago
(2018). We also see a number attraction rate of 10\% which was also
observed in Lago (2018) with close results.

@@

And yes, I plan to beautify the figures.

\begin{figure}[H]
  \begin{floatrow}
    \ffigbox{%

\begin{flushright}\includegraphics{output/figures/unnamed-chunk-1-1} \end{flushright}
    }{\caption{A figure}}

    \btabbox{%

    }{\caption{A table}}
  \end{floatrow}
\end{figure}

@@

In this paper, we have entertained the idea of task effect in the
so-called Turkish number attraction phenomenon. We argue that the
findings of the Lago (2018) study is not clear and there are too many
variables to account for in the experiment, one of them being the
ambiguous morphology that the head noun bears. In the first experiment,
we have replicated the attraction task of Lago (2018). We have found the
similar effects of agreement with a bigger pool of participants. Then,
for entertaining the other possibility in which we argue that
participants do not fully reconstruct the sentence; however, they make
us of the direct cue of overt morpheme \emph{-lAr}, we offer an
experiment where we use object relative clauses as an attractor.

@@

We used the statistical language \texttt{R} (R Core Team 2018) for all
our analyses. These were implemented in dynamic rmarkdown documents
using \texttt{knitr} (Xie 2014, 2015, 2018) and \texttt{rmarkdown}
(Allaire et al. 2018, Xie et al. 2018) packages. All graphs have been
done with \texttt{ggplot} (Wickham 2016). We also would like to thank
Mine Nakipo\u{g}lu and Kadir Gökgöz for giving us the oppurtunity to
conduct experiments and having participants from their classes.

\section{REFERENCES}\label{references}

\hypertarget{refs}{}
\hypertarget{ref-Allaire_2018}{}
Allaire, J., Y. Xie, J. McPherson, J. Luraschi, K. Ushey, A. Atkins, H.
Wickham, J. Cheng, W. Chang, and R. Iannone. 2018. Rmarkdown: Dynamic
documents for r.

\hypertarget{ref-Lago}{}
Lago, S. 2018. Straight from the horse's mouth: agreement attraction
effects with Turkish possessors.

\hypertarget{ref-R_Core_Team_2018}{}
R Core Team. 2018. R: A language and environment for statistical
computing. R Foundation for Statistical Computing, Vienna, Austria.

\hypertarget{ref-Wagers2009}{}
Wagers, M. W., E. F. Lau, and C. Phillips. 2009. Agreement attraction in
comprehension: Representations and processes. Journal of Memory and
Language 61:206--237.

\hypertarget{ref-Wickham_2016}{}
Wickham, H. 2016. Ggplot2: Elegant graphics for data analysis.
Springer-Verlag New York.

\hypertarget{ref-woolford}{}
Woolford, E. 2009. Differential subject marking at argument structure,
syntax, and pf. Pages 17--40 \emph{in} Differential subject marking.
Springer.

\hypertarget{ref-Xie_2014}{}
Xie, Y. 2014. Knitr: A comprehensive tool for reproducible research in
R. \emph{in} V. Stodden, F. Leisch, and R. D. Peng, editors.
Implementing reproducible computational research. Chapman; Hall/CRC.

\hypertarget{ref-Xie_2015}{}
Xie, Y. 2015. Dynamic documents with R and knitr. 2nd editions. Chapman;
Hall/CRC, Boca Raton, Florida.

\hypertarget{ref-Xie_2018}{}
Xie, Y. 2018. Knitr: A general-purpose package for dynamic report
generation in r.

\hypertarget{ref-Xie_2018a}{}
Xie, Y., J. Allaire, and G. Grolemund. 2018. R markdown: The definitive
guide. Chapman; Hall/CRC, Boca Raton, Florida.

\eleft

\listoftables

\listoffigures

>>>>

\documentclass[doc]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes},
            pdfauthor={Utku Türk~\& Pavel Logačev},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural
Morphemes}
    \author{Utku Türk\textsuperscript{1}~\& Pavel Logačev\textsuperscript{1}}
    \date{}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{xcolor}
\usepackage{hhline}
\usepackage{mathtools}
\usepackage{gb4e}\noautomath

\authornote{Add complete departmental affiliations for each
author here. Each new line herein must be indented, like this line.
Enter author note here.

Correspondence concerning this article should be addressed to Utku Türk,
Postal address. E-mail:
\href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}}

\abstract{
This paper deals with agreement attraction because it's more important
than literally anything else. Recently, Lago et al. (2018) demonstrated
agreement attraction effects in comprension in Turkish, which is
super-interesting because this finding allows us to make a lot of money.
However, there is an alternative explanation for their findings: dark
sorcery. In this paper we tested the predictions of these alternative
accounts. In Experiment 1, we found that a particular kind of dark
sorcery was not involved. In Experiment 2, we shall find \ldots{}

}

\begin{document}
\maketitle

@@

\section{Experiment 1}\label{experiment-1}

In their study, Lago (2018) investigates the comprehension of
subject-verb agreement Turkish monolinguals. They use speeded
acceptability judgments for the effects of number attraction in Turkish.
Their sentences make us of genitive-possessive constructions in the
subject position, where the genitive is the attractor and the possessive
is the head noun. They manipulate the grammaticality of the sentence by
changing the plural morphology of the verb, and they also manipulate the
plurality of the attractor noun. In grammatical conditions, the subject
and the verb both bear singular morphology with no overt morpheme.
Moreover, in the ungrammatical conditions, the verb bears the overt
\emph{-lAr} morpheme whereas the subject is still singular as
exemplified below.

\begin{exe}
\ex
\begin{xlist}

\ex \textsc{Ungrammatical, SG attractor} \label{lago4}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singer's backup vocalist jumped on the stage non-stop.

\ex \textsc{Grammatical, PL attractor} \label{lago2}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singers' backup vocalist jumped on the stage non-stop.

\ex \textsc{Ungrammatical, PL attractor} \label{lago3}
\gll \c{S}ark{\i}c{\i}-lar-{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}-lar.\\
singer-\textsc{pl}-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-\textsc{3Pl}\\
\glt The singers' backup vocalist jumped on the stage non-stop.

\ex \textsc{Grammatical, SG attractor} \label{lago1}
\gll \c{S}ark{\i}c{\i}-n{\i}n vokalist-i sahne-de s\"{u}rekli z{\i}pla-d{\i}\\
singer-\textsc{gen} vocalist-\textsc{poss} stage-\textsc{loc} non-stop jump-\textsc{pst}-$\varnothing$\\
\glt The singer's backup vocalist jumped on the stage non-stop.

@@

One hundred and seven Turkish speakers with a mean age of X were
recruited from Bogazici University in İstanbul. We did not collect
participants' knowledge of other languages; however, we verified that
Turkish is their native language and that they predominantly use it in
their daily lives. In the experiments, participants were asked to judge
the acceptability of experimental and filler sentences in Turkish. All
of the sentences were presented one word at a time in the center of the
screen for 500 ms per word unlike Lago (2018) and Wagers, Lau, and
Phillips (2009), in which the duration was 300 ms per word. The
experiment was run on a web-based platform titled the Ibex Farm, and all
of the documentation can be found on our osf and github page.

@@

In \textsc{Figure} (1), the y-axis shows the percentage of
``acceptable'' answers, and the x-axis indicates whether or not the
sentences in that group are grammatical. Moreover, the linet ypes
indicate an attractor noun with overt plural morphology. As seen in the
figure, 1\% of the sentences with plural attractors and a singular verb
were accepted by the participants, in line with the findings of Lago
(2018). We also see a number attraction rate of 2\% which was also
observed in Lago (2018) with close results.

@@

\subsection{Responses}\label{responses}

\begin{figure}
\centering
\includegraphics{AgreementAttraction_files/figure-latex/exp1AvgResponse-1.pdf}
\caption{\label{fig:exp1AvgResponse}Estimates and 95\% credible intervals
for the analysis of the probability of a `yes' response.}
\end{figure}

\begin{figure}
\centering
\includegraphics{AgreementAttraction_files/figure-latex/exp1AvgResponseLagoEtAl-1.pdf}
\caption{\label{fig:exp1AvgResponseLagoEtAl}Estimates and 95\% credible
intervals for the analysis of the probability of a `yes' response.}
\end{figure}

\subsection{Response Times}\label{response-times}

\begin{figure}
\centering
\includegraphics{AgreementAttraction_files/figure-latex/exp1AvgRTs-1.pdf}
\caption{}
\end{figure}

@@

\subsection{\texorpdfstring{In this paper, we have entertained the idea
of task effect in the so-called Turkish number attraction phenomenon. We
argue that the findings of the Lago (2018) study is not clear and there
are too many variables to account for in the experiment, one of them
being the ambiguous morphology that the head noun bears. In the first
experiment, we have replicated the attraction task of Lago (2018). We
have found the similar effects of agreement with a bigger pool of
participants. Then, for entertaining the other possibility in which we
argue that participants do not fully reconstruct the sentence; however,
they make us of the direct cue of overt morpheme \emph{-lAr}, we offer
an experiment where we use object relative clauses as an
attractor.}{In this paper, we have entertained the idea of task effect in the so-called Turkish number attraction phenomenon. We argue that the findings of the Lago (2018) study is not clear and there are too many variables to account for in the experiment, one of them being the ambiguous morphology that the head noun bears. In the first experiment, we have replicated the attraction task of Lago (2018). We have found the similar effects of agreement with a bigger pool of participants. Then, for entertaining the other possibility in which we argue that participants do not fully reconstruct the sentence; however, they make us of the direct cue of overt morpheme -lAr, we offer an experiment where we use object relative clauses as an attractor.}}\label{in-this-paper-we-have-entertained-the-idea-of-task-effect-in-the-so-called-turkish-number-attraction-phenomenon.-we-argue-that-the-findings-of-the-lago-study-is-not-clear-and-there-are-too-many-variables-to-account-for-in-the-experiment-one-of-them-being-the-ambiguous-morphology-that-the-head-noun-bears.-in-the-first-experiment-we-have-replicated-the-attraction-task-of-lago.-we-have-found-the-similar-effects-of-agreement-with-a-bigger-pool-of-participants.-then-for-entertaining-the-other-possibility-in-which-we-argue-that-participants-do-not-fully-reconstruct-the-sentence-however-they-make-us-of-the-direct-cue-of-overt-morpheme--lar-we-offer-an-experiment-where-we-use-object-relative-clauses-as-an-attractor.}

@@

We used the statistical language \texttt{R} (R Core Team, 2018) for all
our analyses. These were implemented in dynamic rmarkdown documents
using \texttt{knitr} (Xie, 2018) and \texttt{rmarkdown} (Xie, Allaire,
\& Grolemund, 2018) packages. All graphs have been done with
\texttt{ggplot} (Wickham, 2016).

\section*{REFERENCES}\label{references}
\addcontentsline{toc}{section}{REFERENCES}

\hypertarget{refs}{}
\hypertarget{ref-Lago}{}
Lago, S. (2018). Straight from the horse's mouth: agreement attraction
effects with Turkish possessors. doi:\href{https://doi.org/none}{none}

\hypertarget{ref-R_Core_Team_2018}{}
R Core Team. (2018). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.
Retrieved from \url{https://www.R-project.org/}

\hypertarget{ref-Wagers2009}{}
Wagers, M. W., Lau, E. F., \& Phillips, C. (2009). Agreement attraction
in comprehension: Representations and processes. \emph{Journal of Memory
and Language}, \emph{61}(2), 206--237.
doi:\href{https://doi.org/10.1016/j.jml.2009.04.002}{10.1016/j.jml.2009.04.002}

\hypertarget{ref-Wickham_2016}{}
Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
Springer-Verlag New York. Retrieved from \url{http://ggplot2.org}

\hypertarget{ref-Xie_2018}{}
Xie, Y. (2018). \emph{Knitr: A general-purpose package for dynamic
report generation in r}. Retrieved from \url{https://yihui.name/knitr/}

\hypertarget{ref-Xie_2018a}{}
Xie, Y., Allaire, J., \& Grolemund, G. (2018). \emph{R markdown: The
definitive guide}. Boca Raton, Florida: Chapman; Hall/CRC. Retrieved
from \url{https://bookdown.org/yihui/rmarkdown}
